invivoPKfit analysis of CvTdb data

### 2023-02-01 Working Rmds/MainAnalysis.Rmd
Adding upper bounds because L-BFGS-B sometimes fails without them (returning NA for optimized param values, but not failing with an error). Adding more detail in output data.frame (including number of points in "empirical" absorption and elimination phases).

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =names_list,
                       defaults_list =   defaults_list,
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       impute_loq = TRUE,
                       impute_sd = TRUE,
                       study_def = c("DTXSID", "Species", "Reference", "Route", "Media"),
                       suppress.messages = TRUE)

@@

```{r}
for(this_rescale_time in c(FALSE, TRUE)){
  for(this_fit_conc_dose in c(FALSE, TRUE)){
    for(this_fit_log_conc in c(FALSE, TRUE)){
      if(!(this_rescale_time %in% FALSE &
           this_fit_conc_dose %in% FALSE &
           this_fit_log_conc %in% FALSE)){ #already did the all FALSE case
      for (this_model in c("flat",
                           "1compartment",
                           "2compartment")){
        print(paste0("model = ", this_model, "\n",
                     "fit_log_conc = ", this_fit_log_conc, "\n",
                     "fit_conc_dose = ", this_fit_conc_dose, "\n",
                     "rescale_time = ", this_rescale_time))
        system.time(
          PK.fit.table <- fit_all(
            data.set = cvt,
            model = this_model,
            modelfun = "analytic",
            preprocess = FALSE,
            fit_conc_dose = this_fit_conc_dose,
            fit_log_conc = this_fit_log_conc,
            rescale_time = this_rescale_time,
            optimx_args = list(
              "method" = "bobyqa",
              "itnmax" = 1e6,
              "control" = list("kkt" = FALSE)
            ),
            suppress.messages = FALSE
          )
        )

        write.csv(PK.fit.table,
                  paste("../inst/ext/PK_fit_table_",
                        this_model,
                        "_fit_log_conc_",
                        this_fit_log_conc, "_",
                        "_fit_conc_dose_",
                        this_fit_conc_dose, "_",
                        "_rescale_time_",
                        this_rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

        post_table <- postprocess_data(PK_fit = PK.fit.table,
                                       model= this_model)

        rm(PK,fit.table)

        write.csv(post_table,
                  paste("../inst/ext/PK_fit_postprocess_",
                        this_model,
                        "_fit_log_conc_",
                        this_fit_log_conc, "_",
                        "_fit_conc_dose_",
                        this_fit_conc_dose, "_",
                        "_rescale_time_",
                        this_rescale_time, "_",
                        timestamp,
                        ".csv",
                        sep=""), row.names = FALSE)

        rm(post_table)
      } #end loop over models
      } #end if not all FALSE
    } #end loop over this_fit_log_conc
  } #end loop over this_fit_conc_dose
} #end loop over this_rescale_time
```

>>>>

```{r}
cvt <- preprocess_data(data.set = cvt_data,
                       names_list =names_list,
                       defaults_list =   defaults_list,
                       ratio_conc_to_dose = 1,
                       calc_loq_factor = 0.45,
                       routes_keep = c("po", "iv"),
                       media_keep = c("blood", "plasma"),
                       impute_loq = TRUE,
                       impute_sd = TRUE,
                       study_def = c("DTXSID", "Species", "Reference"),
                       suppress.messages = TRUE)

@@

```{r}
for(this_method in c("bobyqa", "L-BFGS-B")){
  for(this_rescale_time in c(FALSE, TRUE)){
    for(this_fit_conc_dose in c(FALSE, TRUE)){
      for(this_fit_log_conc in c(FALSE, TRUE)){
          for (this_model in c("flat",
                               "1compartment",
                               "2compartment")){
            cat(paste0("method = ", this_method, "\n",
                         "fit_log_conc = ", this_fit_log_conc, "\n",
                         "fit_conc_dose = ", this_fit_conc_dose, "\n",
                         "rescale_time = ", this_rescale_time, "\n",
                                     "model = ", this_model, "\n"))
            system.time(
              PK.fit.table <- fit_all(
                data.set = cvt,
                model = this_model,
                modelfun = "analytic",
                preprocess = FALSE,
                fit_conc_dose = this_fit_conc_dose,
                fit_log_conc = this_fit_log_conc,
                rescale_time = this_rescale_time,
                optimx_args = list(
                  method = this_method,
                  itnmax = 1e6,
                  control = list(kkt = FALSE,
                                 factr = 1e7)
                ),
                suppress.messages = FALSE
              )
            )

            write.csv(PK.fit.table,
                      paste0("../inst/ext/PK_fit_table_",
                            this_model, "_",
                            "fit_log_conc_",
                            this_fit_log_conc, "_",
                            "fit_conc_dose_",
                            this_fit_conc_dose, "_",
                            "rescale_time_",
                            this_rescale_time, "_",
                            "method_", this_method, "_",
                            timestamp,
                            ".csv"), row.names = FALSE)

          } #end loop over models
      } #end loop over this_fit_log_conc
    } #end loop over this_fit_conc_dose
  } #end loop over this_rescale_time
}#end loop over this_method
```
